\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2011-11-18 doc/USER_MANUAL/manual_SPECFEM3D.tex
manual updates: added Ch 11 on tomographic inversion with kernels; added a couple lines to Table of Contents; added one reference (Maggi2009)

@@

\chapter*{Notes \& Acknowledgments}

@@

\chapter*{Copyright}

@@

\bibliography{bibliography}

>>>>

\chapter{\label{cha:tomo}Tomographic inversion using sensitivity kernels}

One of the fundamental reasons for computing sensitivity kernels (Section~\ref{sec:Adjoint-simulation-finite}) is to use them within a tomographic inversion. In other words, use recorded seismograms, make measurements with synthetic seismograms, and use the misfit between the two to iteratively improve the model described by (at least) $V_{\rm p}$, $V_{\rm s}$, and $\rho$ as a function of space.

Whatever misfit function you use for the tomographic inversion \citep[several examples in][]{Tromp2005}, you will weight the sensitivity kernels with measurements. Furthermore, you will use as many measurements (stations, components, time windows) as possible per event; hence, we call these composite kernels ``event kernels,'' which are volumetric fields representing the gradient of the misfit function with respect to one of the variables (\eg $V_{\rm s}$). The basic features of an adjoint-based tomographic inversion were illustrated in \citet{Tape2007} using a conjugate-gradient algorithm; there are dozens of versions of gradient-based inversion algorithms that could alternatively be used. The tomographic inversion of \citet{Tape2009,Tape2010} used SPECFEM3D as well as several additional components which are also stored on the CIG svn server, described next.

The directory containing utilities for tomographic inversion using SPECFEM3D (or other packages that evaluate misfit functions and gradients) is here on the CIG svn server:
%
\begin{verbatim}
/cig/seismo/3D/ADJOINT_TOMO/
   flexwin/     -- FLEXWIN algorithm for automated picking of time windows
   measure_adj/ -- reads FLEXWIN output file and makes measurements, 
                   with the option for computing adjoint sources
   iterate_adj/ -- various tools for iterative inversion
                   (requires pre-computed "event kernels")
\end{verbatim}
%
This directory also contains a brief \verb+README+ file indicating the role of the three subdirectories, \verb+flexwin+ \citep{Maggi2009}, \verb+measure_adj+, and \verb+iterate_adj+. The components for making the model update are there; however, there are no explicit rules for computing the model update, just as with any optimization problem. There are options for computing a conjugate gradient step, as well as a source subspace projection step. The workflow could use substantial ``stitching together,'' and we welcome suggestions; undoubtedly, the tomographic inversion procedure will improve with time. {\bf This is a work in progress.}

The best single file to read is probably: \verb+ADJOINT_TOMO/iterate_adj/cluster/README+.

%============================================================

@@

\addcontentsline{toc}{chapter}{Notes \& Acknowledgments}
\chapter*{Notes \& Acknowledgments}

@@

\addcontentsline{toc}{chapter}{Copyright}
\chapter*{Copyright}

@@

\addcontentsline{toc}{chapter}{References}
\bibliography{bibliography}
